Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-09 WRITEUP/ms.tex
update sec 3.2

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see Appendix of \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales.
% clouds form in galactic disk typically have virial between 0.2-10 \citep{Dobbs08a, Tasker09a}.

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$
are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.

We also identify MCs in the satellite galaxies of \flower. These MCs
tend to have lower velocity dispersions compared to those of \flower which are more comparable
to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
along the locus of $\sigma\propto R^{0.56}$.
These MCs in the satellite galaxies also have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). Given their low $\alpha_{\rm vir}$ parameter,
these structures are likely collapsing structures.
Based on the $\sigma^2/R - \Sigma$ relation and the virial parameter,
the MCs of the satellite galaxies of
\flower are close to being in virial equilibrium and are unlikely supported against collapse by external pressure.

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds without massive \SF ($<$10\,\Msun) 
in the solar neighborhood ($\lesssim 500$\,pc; Taurus, Perseus, Ophiuchus, and the 
Pipe Nebula) with those with massive \SF in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
with visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase. 
{\bf so...}

@@

\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its cloud size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$200\,\kms (\Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results is therefore robust, haha.

@@

The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band 
(i.e., rest-frame visible) which is between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
Observational studies.. the ... distribution as the cumulative mass function (CMF).
Noisy due to resolution effect, since we only have one galaxy here. However,
we could improve the ``signal-to-noise'' ratio by including clouds identified from different
snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
We fit a power-law to the CMF, expressed in the form of 
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the
highest $n_{\rm cut}$ adopted in this study.
The uncertainties here are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5

>>>>

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see Appendix of \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their velocity dispersions are comparable to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
along the locus of $\sigma\propto R^{0.56}$.
Such high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. 
As shown in \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
%We note that previous studies by 
%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.
In fact, based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales.
On the other hand, the MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
Given the low $\alpha_{\rm vir}$ parameter
and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
these structures are likely collapsing structures.

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
with visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase. 
{\bf so...}

@@

\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$200\,\kms (see \Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results is therefore robust, haha.

@@

The range of masses of the MCs identified are comparable to those observed in \z$\sim$2 galaxies in $i$-band 
(i.e., rest-frame visible), which is between $M_{\rm cl}\approx$10$^{6.5-9xx}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
Observational studies often report the mass distribution in the form of a cumulative function (CMF).
While the CMF of the MCs is quite noisy due to resolution effect and since we only have one galaxy here 
in the cosmological zoom-in simulation, we could improve the ``signal-to-noise ratio'' by including 
MCs identified from the different snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.
Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 
for MCs identified using the lowest and the highest $n_{\rm cut}$ adopted in this study.
The uncertainties here are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
{\bf This means ....}
